Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-02-03 R0V0.tex
Change from "the main advantage" to "one of the main advantages"

\mypara As remarked in \cite{Manchester2014a}, the main advantage to look for control-contraction metric over control-Lyapunov functions is that the former case can be formulate in terms of a convex optimization problem while the latter is non-convex \cite{Rantzer:2001}. The steps to obtain a control to system~\eqref{eq:general system} are recalled below.

>>>>

\mypara As remarked in \cite{Manchester2014a}, one of the main advantages to look for control-contraction metric over control-Lyapunov functions is that the former case can be formulate in terms of a convex optimization problem while the latter is non-convex \cite{Rantzer:2001}. The steps to obtain a control to system~\eqref{eq:general system} are recalled below.
